Indel Historian: fast and accurate ancestral sequence reconstruction

### 2016-10-18 doc/main.tex
edits

\begin{table}
  \begin{tabular}{r|rr|rr}
    & \multicolumn{2}{c|}{BAliBase 3.0} & \multicolumn{2}{c}{PREFAB 4} \\
    & Mean SPS & Mean TCS & Mean SPS & Mean TCS \\
    \hline
Indel Historian & 0.82 & 0.50 & 0.60 & 0.60 \\
CLUSTALW & 0.79 & 0.45 & 0.62 & 0.62 \\
PRANK & 0.73 & 0.35 & 0.51 & 0.51 \\
MAFFT & 0.87 & 0.61 & 0.69 & 0.69 \\
ProbCons & 0.88 & 0.62 & 0.72 & 0.72 \\
MUSCLE & 0.89 & 0.64 & 0.73 & 0.\end{tabular}
  \caption{
    Comparison of Indel Historian to other alignment programs using standard benchmarks
    and the SPS/TCS scores \citep{ThompsonEtAl2005}.
    Average runtime per alignment was 55s for BAliBase and 39s for PREFAB (4 GHz Intel Core i7).
    Data for CLUSTALW, PRANK (+F option, CLUSTALW tree), MAFFT (v6.603), ProbCons (v1.12) and MUSCLE (version 4.0) are from {\tt http://drive5.com/bench/} \citep{Edgar2010}.
  }
\end{table}

@@

In general, Indel Historian performs better on these structure-derived benchmarks than PRANK,
which also performs ancestral reconstruction \citep{LoytynojaGoldman2008},
and is the second-most accurate after ProtPal at estimating indel rates \citep{Westesson2012-zg}.
Compared to leading protein aligners that do not attempt ancestral reconstruction,
Indel Historian outperforms CLUSTALW \citep{LarkinEtAl2007} but not MUSCLE \citep{Edgar2004b},
ProbCons \citep{DoEtAl2005} or MAFFT \citep{KatohEtAl2005}.

>>>>

\begin{table}
  \begin{tabular}{r|rr|rr}
    & \multicolumn{2}{c|}{BAliBase 3.0} & \multicolumn{2}{c}{PREFAB 4} \\
    & Mean SPS & Mean TCS & Mean SPS & Mean TCS \\
    \hline
Indel Historian & 0.82 & 0.50 & 0.60 & 0.60 \\
CLUSTALW & 0.79 & 0.45 & 0.62 & 0.62 \\
PRANK & 0.73 & 0.35 & 0.51 & 0.51 \\
MAFFT & 0.87 & 0.61 & 0.69 & 0.69 \\
ProbCons & 0.88 & 0.62 & 0.72 & 0.72 \\
MUSCLE & 0.89 & 0.64 & 0.73 & 0.73
  \end{tabular}
  \caption{
    Comparison of Indel Historian to other alignment programs using standard benchmarks
    and the SPS/TCS scores \citep{ThompsonEtAl2005}.
    Average runtime per alignment was 55s for BAliBase and 39s for PREFAB (4 GHz Intel Core i7).
    Data for CLUSTALW, PRANK (+F option, CLUSTALW tree), MAFFT (v6.603), ProbCons (v1.12) and MUSCLE (version 4.0) are from {\tt http://drive5.com/bench/} \citep{Edgar2010}.
  }
\end{table}

@@

In general, Indel Historian performs better on these structure-derived benchmarks than PRANK,
which also performs ancestral reconstruction \citep{LoytynojaGoldman2008},
and is the second-most accurate after ProtPal at estimating indel rates \citep{Westesson2012-zg}.
Compared to leading protein aligners that do not attempt ancestral reconstruction,
Indel Historian outperforms CLUSTALW \citep{LarkinEtAl2007} on BaliBase3, but not MUSCLE \citep{Edgar2004b},
ProbCons \citep{DoEtAl2005}, MAFFT \citep{KatohEtAl2005}, or CLUSTALW on PREFAB (though it is close).
